A Comparison of Graph Processing Systems

### 2020-08-22 documentation/paper/main.tex
new plots and some work on testingMethods and results. Also cleaned up Gemini overview

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{textcomp}
\usepackage{pifont}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}

@@

\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)\\
st156571@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)\\
st154960@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{(3341630)\\
@stud.uni-stuttgart.de}}

@@

\begin{abstract}
In this paper we will analyze and compare the graph frameworks Galois, Ligra, Polymer, Gemini and Giraph in their parformance. All the frameworks will be tested in shared memory and Galois, Gemini and Giraph are tested on a distributed cluster as well.
Furthermore we will give some insight on the complexity of writing custom applications based on these frameworks.
\end{abstract}

@@

\section{Introduction}
%\todo
In recent years graph sizes have increased significantly, thus performance and memory efficiency of the graph analysis applications is now more important than ever.

@@

>>>>

\usepackage[noadjust]{cite}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{textcomp}
\usepackage{pifont}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{subcaption}

@@

\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)\\
st156571@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)\\
st154960@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{(3341630)\\
st157100@stud.uni-stuttgart.de}}

@@

\begin{abstract}
In this paper we will analyze and compare the non-uniform memory access (NUMA) aware graph frameworks Galois, Ligra, Polymer and Gemini in their parformance.

Giraph

All the frameworks will be tested in shared memory. Galois, Gemini and Giraph are tested on a distributed cluster as well.
We will give some insight on the calculation performance and associated time overhead of each framework. For this we compare the frameworks in their performance with Single-source shortest-paths, Breadth-first search and PageRank algorithms.
\end{abstract}

@@

\section{Introduction}
In recent years graph sizes have increased significantly, thus performance and memory efficiency of the graph analysis applications is now more important than ever.

We will compare several non-uniform memory access (NUMA) aware systems in terms of their performance on three graph algorithms (PageRank, SSSP, BFS).
The comparison is performed on both real world data sets and synthetic graphs.

To provide a comparison to a non-NUMA aware system, Giraph\cite{Giraph} is included in the testing. Giraph itself has often been compared to other state of the art systems like Pregel or GraphX.

%One of the most famous is the (closed source) distributed graph processing system Pregel. Pregel and several open source versions of .
%This results in suboptimal performance, due to missing cache locality, because the Pregel like systems are written in an object oriented manner relying on pointer chasing mechanisms.

To this end several non-uniform memory access (NUMA) aware systems were proposed like Polymer \cite{Polymer}, Galois \cite{Galois} or Ligra \cite{Ligra}.

@@

\clearpage

### 2020-08-22 documentation/paper/sections/overview/gemini.tex
new plots and some work on testingMethods and results. Also cleaned up Gemini overview

Gemini\cite{Gemini} is a framework for parallel graph processing. In comparrison to the other NUMA-aware frameworks we discuss here Gemini does's not support shared memory parallel processing, it is completely message based using MPI. It seems to be very lightweight and has only the very basically needed functionallity implemented, which leeds to clear source code and small binarys. A basic API hides data and computation distribution details from the user writing applications. It comes with five algorithms already implemented included the three we are testing in this paper. While setting it up and even while benchmarking we had various problems with bugs in the source code, like non zero terminated strings and missing return statements. While debugging we forked the origional repository and made our changes there. DODO link repository.

>>>>

Gemini is a framework for parallel graph processing\cite{Gemini}.
In comparison to the other NUMA-aware frameworks we discuss here, Gemini does not support shared memory parallel processing.
Computation is entirely message based using MPI.
Gemini is lightweight and only provides basic functionality.
A basic API hides data and computation distribution details from the user writing applications.
There are five algorithms (which ones?) already implemented.

### 2020-08-22 documentation/paper/sections/testingMethods.tex
new plots and some work on testingMethods and results. Also cleaned up Gemini overview

\subsection{Graphs}
The graphs used in our testing can be seen in detail in \autoref{tbl:graphs}. We included a variaty of different graph sizes, from relatively small graphs like the flickr graph up to an rMat28 with $4.2$ billion edges. All graphs except the rMat27 and rMat28 are exemplary real-world graphs and were retrieved from the graph database\footnote{\url{http://konect.uni-koblenz.de/}} associated with the Koblenz Network Collection (KONECT)\cite{konect}.
Both the rMat27 and rMat28 were created with a modified version (we changed the output format to EdgeList) of a graph generator provided by Ligra.
\begin{table}
	\caption{Size comparison of the used graphs}
	\label{tbl:graphs}
	\centering
	\begin{tabular}{crr}
		\hline
		\bf{Graph}&\# Vertices (M)&\# Edges (M)\\\hline
		flickr&    		0.1&  2\\
		orkut&          3&    117\\
		wikipedia&      12&   378\\
		twitter&     	52&   1963\\
		rMat27&         63&   2147\\
		friendster&     68&   2586\\
		rMat28&         121&  4294\\
		\hline
	\end{tabular}
\end{table}

\subsection{Algorithms}
We ran Breadth-first search (BFS), PageRank (PR) and Single-source shortest-path (SSSP) algorithms on each framework and graph.
For frameworks that support multiple implementations (e.g. PageRank in push and pull modes), we included the alternatives in our testing. 
\autoref{tbl:algorithms} shows the tested algorithms in detail.
\newcommand{\txtdag}{\textsuperscript{\textdagger}}
\begin{table}
	\caption{Tested algorithms of the frameworks}
	\label{tbl:algorithms}
	\centering
	\begin{tabularx}{\columnwidth}{cYYYYY}
		\bf{Algorithm}&\rot{Galois}&\rot{Gemini}&\rot{Giraph}&\rot{Ligra}&\rot{Polymer}\\\hline
		PageRank&$\Delta$Push, $\Delta$Pull&&&&\\
		SSSP&?, Push, Pull&&&&\\
		BFS&Yes&&*&&\\
		\hline
	\end{tabularx}

>>>>

\subsection{Graphs}
The graphs used in our testing can be seen in detail in \autoref{tbl:graphs}. We included a variaty of different graph sizes, from relatively small graphs like the flickr graph up to an rMat28 with $4.2$ billion edges. All graphs except the rMat27 and rMat28 are exemplary real-world graphs and were retrieved from the graph database\footnote{\url{http://konect.uni-koblenz.de/}} associated with the Koblenz Network Collection (KONECT)\cite{konect}.
Both the rMat27 and rMat28 were created with a modified version (we changed the output format to EdgeList) of a graph generator provided by Ligra.
\begin{table}
	\centering
	\begin{tabular}{crr}
		\hline
		\bf{Graph}&\# Vertices (M)&\# Edges (M)\\\hline
		flickr&    		0.1&  2\\
		orkut&          3&    117\\
		wikipedia&      12&   378\\
		twitter&     	52&   1963\\
		rMat27&         63&   2147\\
		friendster&     68&   2586\\
		rMat28&         121&  4294\\
		\hline
	\end{tabular}
	\caption{Size comparison of the used graphs}
	\label{tbl:graphs}
\end{table}

\subsection{Algorithms}
We ran Breadth-first search (BFS), PageRank (PR) and Single-source shortest-path (SSSP) algorithms on each framework and graph.
For frameworks that support multiple implementations (e.g. PageRank in push and pull modes), we included the alternatives in our testing. 
\autoref{tbl:algorithms} shows the tested algorithms in detail.
\newcommand{\txtdag}{\textsuperscript{\textdagger}}
\begin{table}
	\centering
	\begin{tabularx}{0.9\columnwidth}{cYYYYY}
		\bf{Algorithm}&Galois&Gemini&Giraph&Ligra&Polymer\\\hline
		PageRank&$\Delta$Push, $\Delta$Pull&&&&\\
		SSSP&?, Push, Pull&&&&\\
		BFS&Yes&&*&&\\
		\hline
	\end{tabularx}
	\caption{Tested algorithms of the frameworks}
	\label{tbl:algorithms}
